Improving Haskell Theory Exploration

### 2015-12-09 TransferReport/contributions.tex
Fixes

We adapt the methodology of \emph{recurrent clustering} suggested in CITE, and suggest a new recurrent clustering and feature extraction algorithm for Haskell \iffalse TODO: Fix the end of this sentence \fi theory exploration. As a clustering algorithm, the aim of recurrent clustering is to identify similarities in a set of data points (in our case, Core expressions). Its distinguishing characteristic is to \emph{combine} feature extraction and clustering into a single recursive algorithm (shown as algorithm \ref{alg:recurrent}), which goes beyond a simple syntactic characterisation, to allow the features of an expression to depend on those it references. Here we describe our approach to recurrent clustering and compare its similarity and differences to those of ML4PG and ACL2(ml).

>>>>

We adapt the methodology of \emph{recurrent clustering} proposed in \citep{DBLP:journals/corr/HerasK14, heras2013proof}, and suggest a new recurrent clustering and feature extraction algorithm for Haskell \iffalse TODO: Fix the end of this sentence \fi theory exploration. As a clustering algorithm, the aim of recurrent clustering is to identify similarities in a set of data points (in our case, Core expressions). Its distinguishing characteristic is to \emph{combine} feature extraction and clustering into a single recursive algorithm (shown as algorithm \ref{alg:recurrent}), which goes beyond a simple syntactic characterisation, to allow the features of an expression to depend on those it references. Here we describe our approach to recurrent clustering and compare its similarity and differences to those of ML4PG and ACL2(ml).

### 2015-12-09 TransferReport/related.tex
Fixes

\iffalse TODO: Talk about MuCheck \fi

@@

Whilst \S \label{sec:haskell} gave some brief background on Haskell, little consideration was given for why we chose this language rather than, for example Coq or ACL2 (for which recurrent clustering algorithms already exist), or a more widespread language like Java. Here we discuss the relevant language features from a high-level, which motivated our choice:

@@

\iffalse
TODO
\subsection{Conjecture Generation}

The task of \emph{conjecture generation} lies at the heart of theory exploration, and whilst its main use has been for lemma generation (i.e. performing ) and even significant theorems.

\fi

>>>>

@@

Whilst \S \ref{sec:haskell} gave some brief background on Haskell, little consideration was given for why we chose this language rather than, for example Coq or ACL2 (for which recurrent clustering algorithms already exist), or a more widespread language like Java. Here we discuss the relevant language features from a high-level, which motivated our choice:

@@
